\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This work aims to contribute to the knowledge of Category 7 ("Galaxies with Jets") in the Arp & Madore Catalog of Peculiar Galaxies ("A Catalog of Southern Peculiar Galaxies and Association, 1987"). In particular,
(E) similar to elliptic (E-like), spiral (S), other types (X), and companions (C), present a peculiar peculiar physical process (jets ) which is not yet fully understood for the objects assembled in this Category. Therefore, in order to promote this discussion, we gathered from the literature a set of photometric data (in several spectral bands) and spectroscopic (in the optical), where we infer some correlations of color and nuclear activity for the sample. Spectroscopic data from
were also obtained for some objects in the OPD/LNA-MCTIC. However, since the original observations made by Arp & Madore were obtained with photographic plates, we decided to punctuate some criteria that would guarantee if, in fact, the cataloged objects had jets or if they were other characteristic that
they resemble jets. Or, if they were peculiarities like tails, ties of matter and / or debris, which are included in Category 15 of the Catalog. The 125 final spectra obtained, 52 with absorption lines and 73 with emission lines, were analyzed with the STARLIGHT code of spectral synthesis, which provided a vector
containing the stellar populations present, as well as the ages and metallicities. Although these spectra do not contain information of the jets (weak in their large
majority), we have obtained some preliminary analyzes based on current knowledge about the relativistic jets emissions present in radiogalaxies. Like the
possible physical processes that can characterize the peculiarities observed in Arp & Madore objects come from collision-type gravitational interactions,
fusion, or tide, we believe that the black holes thus formed and that inhabit the center of these objects also represent a key mechanism to explain the
presence of the observed jets, but with the proviso that they accrete gas in the vicinity at low accretion rates. Finally, in order to keep the
discussion of this work, a Web platform was constructed with all the information and data of this dissertation. Photometric and spectroscopic contributions may
be fed by external researchers who have an interest in understanding the peculiar nature of these objects.

\vspace{.5cm}

\textbf{Keywords:} Peculiar Galaxies. Jets. Spectral Synthesis. Data Reduction.
